Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Confound analysis

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of 200 ms duration.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame
% convolving
Events for all regressors of the movie and audio-description stimulus were convolved with a double
gamma hemodynamic response function (HRF).

% we checked correlations
Since we annotated events in fixed time courses, the modeled hemodynamic
time-series could be correlated leading to shared variance and thus low
detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio track of the
audio-description is the audio track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise general linear model (GLM)
$t$-contrasts similarly to previous studies that used controlled stimuli.

>>>>

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of \unit[200]{ms} duration,
%
speech events from onset to offset of each word, and frame-based confounds from
onset to offset of the corresponding movie frame.
% convolving
For all regressors, the stimulus models were convolved with a double-gamma
hemodynamic response function (HRF), as implemented in FSL.

% we checked correlations
Given the unknown confound structure of the naturalistic stimuli we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Figure \ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli
Maximum correlations are found for auditory low-level confounds across stimuli
(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
\texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
Given that all planned voxel-wise general linear models (GLM) exclusively involve
regressors from one of the naturalistic stimuli, the observed correlation
pattern does not indicate problematic confounds of nuissance variables and
regressors of interest.
